Technical Report

### 2018-04-06 fully-abstract-comp/technical-report.tex
Add a note about definitions of programs, components, contexts.

Two programs $\var{comp}$ and $(\var{comp}', c_{\mathrm{main},c}, c_{\mathrm{main},d})$ can be linked into a new program $(\var{comp} \bowtie \var{comp'}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$.
\end{definition}

>>>>

Two programs $\var{comp}$ and $(\var{comp}', c_{\mathrm{main},c}, c_{\mathrm{main},d})$ can be linked into a new program $(\var{comp} \bowtie \var{comp'}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$.
\end{definition}
\dominique{A program is intuitively a component that is ready to be run.  From that point of view, I don't see the point of a program without main. I would propose changing the definitions: a program should be a component that is ready to be executed, i.e. it must have an empty import list and a pair of capabilities to be used as main. A component can be either a component with a main (i.e. a program that still needs to be linked with library implementations) or one without (i.e. a library implementation that will be used by other components). A context for a given component is any other component that can be linked with it to produce a program.}
